```{r}
setwd("C:/dir") #Setting the Environment
data=read.table("Cluster_New.csv", header=TRUE, row.names=1, dec=".", sep=",") #Reading the Table
library(factoextra) #Loading factoextra library
```
```{r}
dismat1<-dist(data, method = "euclidean") # Calculating the distance, using Euclidean method
cluster1<-hclust(dismat1, method = "ward.D") #Using ward.D method of Clustering
plot(cluster1, cex = 0.5)
dev.copy(png,"Euclidean_Plots/Euclidean_with_Wardd.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat1<-dist(data, method = "euclidean") # Calculating the distance, using Euclidean method
cluster2<-hclust(dismat1, method = "ward.D2") #Using ward.D2 method of Clustering
plot(cluster2, cex = 0.5)
fviz_dend(cluster2, k = 4, cex = 0.5, k_colors = c("blue", "skyblue", "red"), color_labels_by_k = TRUE, rect = TRUE)
dev.copy(png,"Euclidean_Plots/Euclidean_with_Wardd2.png", units='in', width=8.5,height=6,res=1200)
 #Saving the Image
```
```{r}
dismat1<-dist(data, method = "euclidean") # Calculating the distance, using Euclidean method
cluster3<-hclust(dismat1, method = "single") #Using ward.D method of Clustering
plot(cluster3, cex = 0.5)
dev.copy(png,"Euclidean_Plots/Euclidean_with_single.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat1<-dist(data, method = "euclidean") # Calculating the distance, using Euclidean method
cluster4<-hclust(dismat1, method = "complete") #Using ward.D method of Clustering
plot(cluster4, cex = 0.5)
dev.copy(png,"Euclidean_Plots/Euclidean_with_complete.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat1<-dist(data, method = "euclidean") # Calculating the distance, using Euclidean method
cluster5<-hclust(dismat1, method = "average") #Using ward.D method of Clustering
plot(cluster5, cex = 1)
fviz_dend(cluster5, k = 3, cex = 0.5, k_colors = c("blue", "skyblue", "red"), color_labels_by_k = TRUE, rect = TRUE)
dev.copy(png,"Euclidean_Plots/Euclidean_with_average_New.png", units='in', width=8.5,height=6,res=1200)
 #Saving the Image
```
```{r}
dismat1<-dist(data, method = "euclidean") # Calculating the distance, using Euclidean method
cluster6<-hclust(dismat1, method = "mcquitty") #Using ward.D method of Clustering
plot(cluster6, cex = 0.5)
dev.copy(png,"Euclidean_Plots/Euclidean_with_mcquitty.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat1<-dist(data, method = "euclidean") # Calculating the distance, using Euclidean method
cluster7<-hclust(dismat1, method = "median") #Using ward.D method of Clustering
plot(cluster7, cex = 0.5)
dev.copy(png,"Euclidean_Plots/Euclidean_with_median.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat1<-dist(data, method = "euclidean") # Calculating the distance, using Euclidean method
cluster8<-hclust(dismat1, method = "centroid") #Using ward.D method of Clustering
plot(cluster8, cex = 0.5)
dev.copy(png,"Euclidean_Plots/Euclidean_with_centroid.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat2<-dist(data, method = "maximum") # Calculating the distance, using maximum method
cluster1b<-hclust(dismat2, method = "ward.D") #Using ward.D method of Clustering
plot(cluster1b, cex = 0.5)
fviz_dend(cluster1b, k = 3, cex = 0.5, k_colors = c("blue", "skyblue", "red"), color_labels_by_k = TRUE, rect = TRUE)
dev.copy(png,"Maximum_Plots/Maximum_with_Wardd.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```{r}
dismat2<-dist(data, method = "maximum") # Calculating the distance, using maximum method
cluster2b<-hclust(dismat2, method = "ward.D2") #Using ward.D2 method of Clustering
plot(cluster2b, cex = 0.5)
dev.copy(png,"Maximum_Plots/Maximum_with_Wardd2.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat2<-dist(data, method = "maximum") # Calculating the distance, using maximum method
cluster3b<-hclust(dismat2, method = "single") #Using ward.D method of Clustering
plot(cluster3b, cex = 0.5)
dev.copy(png,"Maximum_Plots/Maximum_with_single.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat2<-dist(data, method = "maximum") # Calculating the distance, using maximum method
cluster4b<-hclust(dismat2, method = "complete") #Using ward.D method of Clustering
plot(cluster4b, cex = 0.5)
dev.copy(png,"Maximum_Plots/Maximum_with_complete.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat2<-dist(data, method = "maximum") # Calculating the distance, using maximum method
cluster5b<-hclust(dismat2, method = "average") #Using ward.D method of Clustering
plot(cluster5b, cex = 0.5)
dev.copy(png,"Maximum_Plots/Maximum_with_average.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat2<-dist(data, method = "maximum") # Calculating the distance, using maximum method
cluster6b<-hclust(dismat2, method = "mcquitty") #Using ward.D method of Clustering
plot(cluster6b, cex = 0.5)
dev.copy(png,"Maximum_Plots/Maximum_with_mcquitty.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat2<-dist(data, method = "maximum") # Calculating the distance, using maximum method
cluster7b<-hclust(dismat2, method = "median") #Using ward.D method of Clustering
plot(cluster7b, cex = 0.5)
dev.copy(png,"Maximum_Plots/Maximum_with_median.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat2<-dist(data, method = "maximum") # Calculating the distance, using maximum method
cluster8b<-hclust(dismat2, method = "centroid") #Using ward.D method of Clustering
plot(cluster8b, cex = 0.5)
dev.copy(png,"Maximum_Plots/Maximum_with_centroid.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat3<-dist(data, method = "manhattan") # Calculating the distance, using manhattan method
cluster1c<-hclust(dismat3, method = "ward.D") #Using ward.D method of Clustering
plot(cluster1c, cex = 0.5)
dev.copy(png,"Manhattan_Plots/Manhattan_with_Wardd.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat3<-dist(data, method = "manhattan") # Calculating the distance, using manhattan method
cluster2c<-hclust(dismat3, method = "ward.D2") #Using ward.D2 method of Clustering
plot(cluster2c, cex = 0.5)
dev.copy(png,"Manhattan_Plots/Manhattan_with_Wardd2.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat3<-dist(data, method = "manhattan") # Calculating the distance, using manhattan method
cluster3c<-hclust(dismat3, method = "single") #Using ward.D method of Clustering
plot(cluster3c, cex = 0.5)
dev.copy(png,"Manhattan_Plots/Manhattan_with_single.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat3<-dist(data, method = "manhattan") # Calculating the distance, using manhattan method
cluster4c<-hclust(dismat3, method = "complete") #Using ward.D method of Clustering
plot(cluster4c, cex = 0.5)
dev.copy(png,"Manhattan_Plots/Manhattan_with_complete.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```

```{r}
dismat3<-dist(data, method = "manhattan") # Calculating the distance, using manhattan method
cluster5c<-hclust(dismat3, method = "average") #Using ward.D method of Clustering
plot(cluster5c, cex = 0.5)
dev.copy(png,"Manhattan_Plots/Manhattan_with_average.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat3<-dist(data, method = "manhattan") # Calculating the distance, using manhattan method
cluster6c<-hclust(dismat3, method = "mcquitty") #Using ward.D method of Clustering
plot(cluster6c, cex = 0.5)
dev.copy(png,"Manhattan_Plots/Manhattan_with_mcquitty.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat3<-dist(data, method = "manhattan") # Calculating the distance, using manhattan method
cluster7c<-hclust(dismat3, method = "median") #Using ward.D method of Clustering
plot(cluster7c, cex = 0.5)
dev.copy(png,"Manhattan_Plots/Manhattan_with_median.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat3<-dist(data, method = "manhattan") # Calculating the distance, using manhattan method
cluster8c<-hclust(dismat3, method = "centroid") #Using ward.D method of Clustering
plot(cluster8c, cex = 0.5)
dev.copy(png,"Manhattan_Plots/Manhattan_with_centroid.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat4<-dist(data, method = "canberra") # Calculating the distance, using canberra method
cluster1d<-hclust(dismat4, method = "ward.D") #Using ward.D method of Clustering
plot(cluster1d, cex = 0.5)
dev.copy(png,"Canberra_Plots/Canberra_with_Wardd.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat4<-dist(data, method = "canberra") # Calculating the distance, using canberra method
cluster2d<-hclust(dismat4, method = "ward.D2") #Using ward.D2 method of Clustering
plot(cluster2d, cex = 0.5)
dev.copy(png,"Canberra_Plots/Canberra_with_Wardd2.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat4<-dist(data, method = "canberra") # Calculating the distance, using canberra method
cluster3d<-hclust(dismat4, method = "single") #Using ward.D method of Clustering
plot(cluster3d, cex = 0.5)
dev.copy(png,"Canberra_Plots/Canberra_with_single.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat4<-dist(data, method = "canberra") # Calculating the distance, using canberra method
cluster4d<-hclust(dismat4, method = "complete") #Using ward.D method of Clustering
plot(cluster4d, cex = 0.5)
dev.copy(png,"Canberra_Plots/Canberra_with_complete.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat4<-dist(data, method = "canberra") # Calculating the distance, using canberra method
cluster5d<-hclust(dismat4, method = "average") #Using ward.D method of Clustering
plot(cluster5d, cex = 0.5)
dev.copy(png,"Canberra_Plots/Canberra_with_average.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat4<-dist(data, method = "canberra") # Calculating the distance, using canberra method
cluster6d<-hclust(dismat4, method = "mcquitty") #Using ward.D method of Clustering
plot(cluster6d, cex = 0.5)
dev.copy(png,"Canberra_Plots/Canberra_with_mcquitty.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat4<-dist(data, method = "canberra") # Calculating the distance, using canberra method
cluster7d<-hclust(dismat4, method = "median") #Using ward.D method of Clustering
plot(cluster7d, cex = 0.5)
dev.copy(png,"Canberra_Plots/Canberra_with_median.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat4<-dist(data, method = "canberra") # Calculating the distance, using canberra method
cluster8d<-hclust(dismat4, method = "centroid") #Using ward.D method of Clustering
plot(cluster8d, cex = 0.5)
dev.copy(png,"Canberra_Plots/Canberra_with_centroid.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat5<-dist(data, method = "binary") # Calculating the distance, using binary method
cluster1e<-hclust(dismat5, method = "ward.D") #Using ward.D method of Clustering
plot(cluster1e, cex = 0.5)
dev.copy(png,"Binary_Plots/binary_with_Wardd.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat5<-dist(data, method = "binary") # Calculating the distance, using binary method
cluster2e<-hclust(dismat5, method = "ward.D2") #Using ward.D2 method of Clustering
plot(cluster2e, cex = 0.5)
dev.copy(png,"Binary_Plots/binary_with_Wardd2.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat5<-dist(data, method = "binary") # Calculating the distance, using binary method
cluster3e<-hclust(dismat5, method = "single") #Using ward.D method of Clustering
plot(cluster3e, cex = 0.5)
dev.copy(png,"Binary_Plots/binary_with_single.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat5<-dist(data, method = "binary") # Calculating the distance, using binary method
cluster4e<-hclust(dismat5, method = "complete") #Using ward.D method of Clustering
plot(cluster4e, cex = 0.5)
dev.copy(png,"Binary_Plots/binary_with_complete.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat5<-dist(data, method = "binary") # Calculating the distance, using binary method
cluster5e<-hclust(dismat5, method = "average") #Using ward.D method of Clustering
plot(cluster5e, cex = 0.5)
dev.copy(png,"Binary_Plots/binary_with_average.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat5<-dist(data, method = "binary") # Calculating the distance, using binary method
cluster6e<-hclust(dismat5, method = "mcquitty") #Using ward.D method of Clustering
plot(cluster6e, cex = 0.5)
dev.copy(png,"Binary_Plots/binary_with_mcquitty.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```

```{r}
dismat5<-dist(data, method = "binary") # Calculating the distance, using binary method
cluster7e<-hclust(dismat5, method = "median") #Using ward.D method of Clustering
plot(cluster7e, cex = 0.5)
dev.copy(png,"Binary_Plots/binary_with_median.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat5<-dist(data, method = "binary") # Calculating the distance, using binary method
cluster8e<-hclust(dismat5, method = "centroid") #Using ward.D method of Clustering
plot(cluster8e, cex = 0.5)
dev.copy(png,"Binary_Plots/binary_with_centroid.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat6<-dist(data, method = "minkowski") # Calculating the distance, using minkowski method
cluster1f<-hclust(dismat6, method = "ward.D") #Using ward.D method of Clustering
plot(cluster1f, cex = 0.5)
dev.copy(png,"Minkowski_Plots/minkowski_with_Wardd.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat6<-dist(data, method = "minkowski") # Calculating the distance, using minkowski method
cluster2f<-hclust(dismat6, method = "ward.D2") #Using ward.D2 method of Clustering
plot(cluster2f, cex = 0.5)
dev.copy(png,"Minkowski_Plots/minkowski_with_Wardd2.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat6<-dist(data, method = "minkowski") # Calculating the distance, using minkowski method
cluster3f<-hclust(dismat6, method = "single") #Using ward.D method of Clustering
plot(cluster3f, cex = 0.5)
dev.copy(png,"Minkowski_Plots/minkowski_with_single.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat6<-dist(data, method = "minkowski") # Calculating the distance, using minkowski method
cluster4f<-hclust(dismat6, method = "complete") #Using ward.D method of Clustering
plot(cluster4f, cex = 0.5)
dev.copy(png,"Minkowski_Plots/minkowski_with_complete.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat6<-dist(data, method = "minkowski") # Calculating the distance, using minkowski method
cluster5f<-hclust(dismat6, method = "average") #Using ward.D method of Clustering
plot(cluster5f, cex = 0.5)
dev.copy(png,"Minkowski_Plots/minkowski_with_average.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat6<-dist(data, method = "minkowski") # Calculating the distance, using minkowski method
cluster6f<-hclust(dismat6, method = "mcquitty") #Using ward.D method of Clustering
plot(cluster6f, cex = 0.5)
dev.copy(png,"Minkowski_Plots/minkowski_with_mcquitty.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat6<-dist(data, method = "minkowski") # Calculating the distance, using minkowski method
cluster7f<-hclust(dismat6, method = "median") #Using ward.D method of Clustering
plot(cluster7f, cex = 0.5)
dev.copy(png,"Minkowski_Plots/minkowski_with_median.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
```
```{r}
dismat6<-dist(data, method = "minkowski") # Calculating the distance, using minkowski method
cluster8f<-hclust(dismat6, method = "centroid") #Using ward.D method of Clustering
plot(cluster8f, cex = 0.5)
dev.copy(png,"Minkowski_Plots/minkowski_with_centroid.png", units='in', width=8.5,height=6,res=1200) #Saving the Image
#End of the Programme
```

